State of the Practice for Lattice Boltzmann Method Software

### 2021-12-13 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
specified parallel options

\begin{table}
    \begin{center}
        \begin{tabular}{ p{3cm}lllllll}
            \hline
            Name & Dim & Pll & Com & Rflx & Mfl & NN & OS\\
            \hline
            DL\_MESO (LBE) & ? & ? & ? & ? & ? & ? & ?\\
            ESPResSo & ? & ? & ? & ? & ? & ? & ?\\
            ESPResSo++ & ? & ? & ? & ? & ? & ? & ?\\
            lbmpy & ? & ? & ? & ? & ? & ? & ?\\
            lettuce & ? & ? & ? & ? & ? & ? & ?\\
            Ludwig & ? & ? & ? & ? & ? & ? & ?\\
            LUMA & ? & ? & ? & ? & ? & ? & ?\\
            MechSys & ? & ? & ? & ? & ? & ? & ?\\
            OpenLB & ? & ? & ? & ? & ? & ? & ?\\
            Palabos & ? & ? & ? & ? & ? & ? & ?\\
            pyLBM & ? & ? & ? & ? & ? & ? & ?\\
            Sailfish & ? & ? & ? & ? & ? & ? & ?\\
            TCLB & ? & ? & ? & ? & ? & ? & ?\\
            waLBerla & ? & ? & ? & ? & ? & ? & ?\\
            HemeLB & ? & ? & ? & ? & ? & ? & ?\\
            laboetie & ? & ? & ? & ? & ? & ? & ?\\
            LatBo.jl & ? & ? & ? & ? & ? & ? & ?\\
            LB2D-Prime & ? & ? & ? & ? & ? & ? & ?\\
            LB3D & ? & ? & ? & ? & ? & ? & ?\\
            LB3D-Prime & ? & ? & ? & ? & ? & ? & ?\\
            LIMBES & ? & ? & ? & ? & ? & ? & ?\\
            MP-LABS & ? & ? & ? & ? & ? & ? & ?\\
            SunlightLB & ? & ? & ? & ? & ? & ? & ?\\

            \hline
        \end{tabular}
        \caption{Features of Software Packages (Dim for Dimension (1, 2 or 3),
        Pll for Parallel (Yes or No), Com for Compressible (Yes or No), Rflx for
        Reflexive boundary condition (Yes or No), MFl for Multifluid (Yes or
        No), NN for Non-Newtonian, OS (Win, Mac, Lin, )} \label{tbl_features}
    \end{center}
    \end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}llllllll}
			\hline
			Name & Dim & Pll & Com & Rflx & MFl & Turb & CGE & OS\\
			\hline
			DL\_MESO (LBE) & 2, 3 & MPI/OMP & Y & Y & Y & Y & Y & W, M, L\\
			ESPResSo & 1, 2, 3 & CUDA/MPI & Y & Y & Y & Y & Y & M, L\\
			ESPResSo++ & 1, 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			HemeLB & 3 & MPI & Y & Y & Y & Y & Y & L\\
			laboetie & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			LatBo.jl & 2, 3 & - & Y & Y & Y & N & Y & L\\
			LB2D-Prime & 2 & MPI & Y & Y & Y & Y & Y & W, L\\
			LB3D & 3 & MPI & N & Y & Y & Y & Y & L\\
			LB3D-Prime & 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			lbmpy & 2, 3 & CUDA & Y & Y & Y & Y & Y & L\\
			lettuce & 2, 3 & CUDA & Y & Y & Y & Y & Y & W, M, L\\
			LIMBES & 2 & OMP & Y & Y & N & N & Y & L\\
			Ludwig & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			LUMA & 2, 3 & MPI & Y & Y & Y & Y & Y & W, M, L\\
			MechSys & 2, 3 & - & Y & Y & Y & Y & Y & L\\
			MP-LABS & 2, 3 & MPI/OMP & N & Y & Y & N & N & L\\
			OpenLB & 1, 2, 3 & MPI & Y & Y & Y & Y & Y & W, M, L\\
			Palabos & 2, 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			pyLBM & 1, 2, 3 & MPI & Y & Y & N & Y & Y & W, M, L\\
			Sailfish & 2, 3 & CUDA & Y & Y & Y & Y & Y & M, L\\
			SunlightLB & 3 & - & Y & Y & N & N & Y & L\\
			TCLB & 2, 3 & CUDA/MPI & Y & Y & Y & Y & Y & L\\
			waLBerla & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			\hline
		\end{tabular}
		\caption{Features of Software Packages (Dim for Dimension (1, 2, 3),
			Pll for Parallel (CUDA, MPI, OpenMP (OMP)), Com for Compressible (Yes or No), Rflx for
			Reflexive Boundary Condition (Yes or No), MFl for Multifluid (Yes or
			No), Turb for Turbulent (Yes or No), CGE for Complex Geometries (Yes or No), OS for Operating System (Windows (W), macOS (M), Linux (L)))} \label{tbl_features}
	\end{center}
\end{table}
